---
title: "visualization"
output: github_document
---

```{r setup}
library(tidyverse)
library(ggridges)
```

## Load the weather data

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())


weather_df
```


## scatterplot

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) +
  geom_point()
```


NEW APPRAOCH for the same plot
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point()
```



save and edit a plot object
```{r}
weather_plot = 
  weather_df %>% 
  ggplot(aes(x = tmin, y = tmax))

weather_plot + geom_point()
```



## Advanced scatterplot

Start with the same one and make it fancy
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point() +
  geom_smooth(se = FALSE)
```



WHAT ABOUT the 'aes' placement
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(aes(color = name)) +
  geom_smooth()

# 变成一条线 之前3条不同颜色线
```






facet some things
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = 0.2, size = 0.3) +      #alpha --transparency
  geom_smooth(se = FALSE, size = 2) +
  facet_grid(. ~ name)
# 三张图， 各自分开的
# . 表示不增加行，name表示列，因此为一行三列
# 三行一列为 facet_grid(name ~ .)
```

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, alpha = tmin, color = name)) +
  geom_point() +      #alpha --transparency 使得值小的时候浅，值大的时候深
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name)
```



Let's combine some elements and try a new plot

```{r}
weather_df %>% 
  ggplot(aes(x = date, y = tmax, color = name)) +
  gem_point(aes(size = prcp), alpha = 0.5) +   #点的大小和prcp 成正比
  geom_smooth(se =FALSE) +
  facet_grid(. ~ name)
```




##some small notes

how many geoms have to exist?

YOU can have whatever geoms you want.

```{r}
wweather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_smooth(se = FALSE)
```



you can use a neat geom
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_hex()  #菱形的色块
```

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_density2d() + #contour 等高线
  geom_point(alpha = 0.3)
```



## Univariate plots

Histograms are really great
```{r}
weather_df %>% 
  ggplot(aes(x = tmin)) +
  geom_histogram()
```


add color
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, color = name)) + #边框有颜色
  geom_histogram(position = 'dodge')  # 左右排列不同颜色的
```


```{r}
weather_df %>% 
  ggplot(aes(x = tmin, fill = name )) +  #填充有颜色
  geom_histogram(position = 'dodge')
```


```{r}
weather_df %>% 
  ggplot(aes(x = tmin, fill = name )) +  
  geom_histogram() +
  facet_grid(. ~ name)
```




Let's try a new geometry
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, fill = name)) +
  geom_density(alpha = 0.3)
```







What about boxplot?
```{r}
weather_df %>% 
  ggplot(aes(x = name, y = tmin)) +   #x为name，显示三个图
  geom_boxplot()

```
 



Trendy plots
```{r}
weather_df %>% 
  ggolot(aes(x = name, y = tmin, fill = name)) +
  geom_violin(alpha = 0.5) +
  stat_summary()

```




Ridge plot- the most popular plot of 2017
```{r}
weather_df %>% 
  ggolot(aes(x = tmin, y = name)) +
  geom_density_ridges()   # 同一个横坐标
```





## Save and embed

Let's save a scatterplot
```{r}
weather_plot = 
  weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color =name)) +
  geom_point(alpha = 0.5)

ggsave('./results/weather_plot.pdf', weather_plot, width = 8, height = 5)
```



What about embedding
```{r}
weather_plot
```


embed at different size
```{r fig.width=12, fig.height=6}
weather_plot
```










